### 2016-11-08 paper2.tex
Fixed page numbering
Fixed figure sizes
Fixed fancy header for chapters and abstracts
Fixed bibliography issue

\begin{abstract}
        \addcontentsline{toc}{section}{Abstract}
    We present the first cosmological galaxy evolved using the modern smoothed
    particle hydrodynamics (SPH) code \textsc{GASOLINE2} with superbubble
    feedback.  We show that superbubble-driven galactic outflows powered by Type
    II supernovae alone can produce $\rm{L^*}$ galaxies with flat rotation
    curves with circular velocities $\sim 200\; \rm{km/s}$, low bulge-to-disc
    ratios, and stellar mass fractions that match observed values from high
    redshift to the present.  These features are made possible by the high mass
    loadings generated by the evaporative growth of superbubbles.  Outflows are
    driven extremely effectively at high redshift, expelling gas at early times
    and preventing overproduction of stars before $z=2$.  Centrally
    concentrated gas in previous simulations has often lead to unrealistically
    high bulge to total ratios and strongly peaked rotation curves.  We show that
    supernova-powered superbubbles alone can produce galaxies that agree well
    with observed properties without the need for additional feedback mechanisms
    or increased feedback energy.   We present additional results arising from
    properly modelled hot feedback.
\end{abstract}

@@

Today, multiple different models of strong feedback have begun to produce
galaxies with the correct number of stars \citep{Aumer2013}, reasonable star
formation histories \citep{Stinson2013,Agertz2014,Munshi2013}, and correct
morphologies \citep{Guedes2011,Brook2012,Christensen2014}.   Unfortunately, many
of these successes have come at the cost of increasing complexity in star
formation and feedback methods, crude assumptions regarding the physics of the
feedback-heated gas and somewhat arbitrary increases in the feedback energy per
unit mass in stars.

In many cases, strong feedback simply means more energy.  Many modern feedback
models augment the energy input from Type II supernovae ($\sim10^{51}\;
\rm{erg}$ per star above $8\; \rm{M_\odot}$), with that arising from stellar
winds, UV ionization, supermassive black holes (SMBH), or radiation pressure
\citep{Vogelsberger2013, Agertz2014}.  Feedback models such as
\citet{Stinson2013} group these sources of energy as early stellar feedback.
Since the first supernovae occur $\sim4\; \rm{Myr}$ after star formation, these
feedback mechanisms begin depositing feedback before SN-only methods would.
Unfortunately, how much energy from these early feedback effects actually
couples to the surrounding ISM rather than radiating away is highly uncertain.
In fact, even the coupling of comparatively simpler SN feedback still is a
matter of some debate.  Many new feedback models \citep{Agertz2013, Aumer2013,
Hopkins2013} treat each of these feedback mechanisms explicitly, modelling the
input of energy and momentum from each component separately.

@@

We compare four test cases using the same initial conditions: no stellar
feedback (an absolute lower bound for looking at the effects of feedback);
superbubble feedback (our fiducial case); blastwave feedback (the feedback
method used in \citet{Stinson2010}, first described in \citealt{Stinson2006}); and
superbubble feedback with double the standard feedback energy ($2\times10^{51}\;
\rm{erg}$ per SN).  The high feedback energy case uses more feedback than is
predicted by \citet{Leitherer1999}, but is within the range of feedback energies
currently being used in cosmological simulations \citep{Schaye2015, Agertz2014,
Vogelsberger2013}.

@@

    \includegraphics[width=\columnwidth]{figures2/rotation_curve.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/circularity.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/mass_growth.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/stellar_fraction.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/sfr.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/burstiness.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/massloading.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/net_accretion.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/inflowoutflow.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/angular_momentum_netflux.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/angular_momentum_outflow.eps}

@@

    \includegraphics[width=\columnwidth]{figures2/phase.eps}

>>>>

\setcounter{pageFix}{\value{page}}
\begin{abstract}
\thispagestyle{fancy}
    \setcounter{page}{\value{pageFix}}
        \addcontentsline{toc}{section}{Abstract}
    We present the first cosmological galaxy evolved using the modern smoothed
    particle hydrodynamics (SPH) code \textsc{GASOLINE2} with superbubble
    feedback.  We show that superbubble-driven galactic outflows powered by Type
    II supernovae alone can produce $\rm{L^*}$ galaxies with flat rotation
    curves with circular velocities $\sim 200\; \rm{km/s}$, low bulge-to-disc
    ratios, and stellar mass fractions that match observed values from high
    redshift to the present.  These features are made possible by the high mass
    loadings generated by the evaporative growth of superbubbles.  Outflows are
    driven extremely effectively at high redshift, expelling gas at early times
    and preventing overproduction of stars before $z=2$.  Centrally
    concentrated gas in previous simulations has often lead to unrealistically
    high bulge to total ratios and strongly peaked rotation curves.  We show that
    supernova-powered superbubbles alone can produce galaxies that agree well
    with observed properties without the need for additional feedback mechanisms
    or increased feedback energy.   We present additional results arising from
    properly modelled hot feedback.
\end{abstract}

@@

Today, multiple different models of strong feedback have begun to produce
galaxies with the correct number of stars \citep{Aumer2013}, reasonable star
formation histories \citep{Stinson2013,Agertz2015,Munshi2013}, and correct
morphologies \citep{Guedes2011,Brook2012,Christensen2014}.   Unfortunately, many
of these successes have come at the cost of increasing complexity in star
formation and feedback methods, crude assumptions regarding the physics of the
feedback-heated gas and somewhat arbitrary increases in the feedback energy per
unit mass in stars.

In many cases, strong feedback simply means more energy.  Many modern feedback
models augment the energy input from Type II supernovae ($\sim10^{51}\;
\rm{erg}$ per star above $8\; \rm{M_\odot}$), with that arising from stellar
winds, UV ionization, supermassive black holes (SMBH), or radiation pressure
\citep{Vogelsberger2013, Agertz2015}.  Feedback models such as
\citet{Stinson2013} group these sources of energy as early stellar feedback.
Since the first supernovae occur $\sim4\; \rm{Myr}$ after star formation, these
feedback mechanisms begin depositing feedback before SN-only methods would.
Unfortunately, how much energy from these early feedback effects actually
couples to the surrounding ISM rather than radiating away is highly uncertain.
In fact, even the coupling of comparatively simpler SN feedback still is a
matter of some debate.  Many new feedback models \citep{Agertz2013, Aumer2013,
Hopkins2013} treat each of these feedback mechanisms explicitly, modelling the
input of energy and momentum from each component separately.

@@

We compare four test cases using the same initial conditions: no stellar
feedback (an absolute lower bound for looking at the effects of feedback);
superbubble feedback (our fiducial case); blastwave feedback (the feedback
method used in \citet{Stinson2010}, first described in \citealt{Stinson2006}); and
superbubble feedback with double the standard feedback energy ($2\times10^{51}\;
\rm{erg}$ per SN).  The high feedback energy case uses more feedback than is
predicted by \citet{Leitherer1999}, but is within the range of feedback energies
currently being used in cosmological simulations \citep{Schaye2015, Agertz2015,
Vogelsberger2013}.

@@

    \includegraphics[width=\textwidth]{figures2/rotation_curve.eps}

@@

    \includegraphics[width=\textwidth]{figures2/circularity.eps}

@@

    \includegraphics[width=\textwidth]{figures2/mass_growth.eps}

@@

    \includegraphics[width=\textwidth]{figures2/stellar_fraction.eps}

@@

    \includegraphics[width=\textwidth]{figures2/sfr.eps}

@@

    \includegraphics[width=\textwidth]{figures2/burstiness.eps}

@@

    \includegraphics[width=\textwidth]{figures2/massloading.eps}

@@

    \includegraphics[width=\textwidth]{figures2/net_accretion.eps}

@@

    \includegraphics[width=\textwidth]{figures2/inflowoutflow.eps}

@@

    \includegraphics[width=\textwidth]{figures2/angular_momentum_netflux.eps}

@@

    \includegraphics[width=\textwidth]{figures2/angular_momentum_outflow.eps}

@@

    \includegraphics[width=\textwidth]{figures2/phase.eps}
